Digital History in Finland, 1488-1828

### 2017-01-31 inst/examples/20170125-Manuscript-FK.Rmd
analysis updates

```{r linkoping, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
minyear <- 1640
maxyear <- 1828
myplace <- "Linköping"
cat <- "Kungliga"
df <- df0 %>% filter(publication_place == myplace) %>%
      	      filter(catalog == cat) %>%
              filter(publication_year >= minyear &
	             publication_year <= maxyear) #%>%

@@

dfs <- df %>% select(publication_year, publisher) %>%
	      filter(!is.na(publisher)) %>%
              unique %>%	      
	      arrange(publication_year)
kable(dfs)
.```

>>>>

```{r linkoping, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
minyear <- 1640
maxyear <- 1828
myplace <- "Linköping"
cat <- "Kungliga"
df <- df0 %>% filter(publication_place == myplace) %>%
      	      filter(catalog == cat) %>%
              filter(publication_year >= minyear &#
	             publication_year <= maxyear)

@@

dfs <- df %>% select(publication_year, publisher) %>%
	      filter(!is.na(publisher)) %>%
              unique %>%	      
	      arrange(publication_year)
kable(dfs)
```

### 2017-01-31 inst/examples/manuscript-krakow.Rmd
analysis updates

```{r linkoping2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
p <- plot_timeline(data = df, x = "publication_decade", y = "titlecount") +
       ylab("Title count (n)") +
       ggtitle(paste("Title count: ", cat, "/", myplace))
print(p)
.```

>>>>

```{r linkoping2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
p <- plot_timeline(data = df, x = "publication_decade", y = "titlecount") +
       ylab("Title count (n)") +
       ggtitle(paste("Title count: ", cat, "/", myplace))
print(p)
```
